\documentclass{article}[20200304]

\usepackage{amsmath}

\title{Mathematic Symbols}
\author{listenzcc}

\begin{document}

\maketitle

\section{Basic Features}
Basic features of formulas, e.g. How to place formulas properly.

\paragraph{Inline formulas example}
Words before \(B(a, b)\) words after.

\paragraph{Newline formulas example}
Newline formulas example. Words before \[B(a, b)\] words after.

\section{Operators}
Basic operators and symbols.

\paragraph{Examples}

Quad: \(A \quad B\).

Power: \(e^{-b \times c}\).

Sqrt: \(\sqrt{b \times c} \times d\).

Frac: \(\frac{a}{b + c}\).

Others: \(+, -, \times, \div, \pm, \mp\).

\(\cup, \cap, \sqcup, \sqcap, \uplus\).

\(\cdot, \star, \ast, \circ, \bullet, \diamond\).

\(\oplus, \odot, \ominus, \oslash, \bigcirc, \otimes, \bigtriangleup, \bigtriangledown, \triangleleft, \triangleright\).

\(\vee, \wedge, \amalg, \dagger, \ddagger, \wr\).

\section{Set Operators}
Set operators.

\paragraph{Examples}

Forall: \(\forall a\).

Exists: \(\exists a\).

In: \(a \in A\).

NotIn: \(A \notin B\).

Union: \(\bigcup A\).

Inter: \(\bigcap A\).

Minus: \(A \setminus B\).

Empty: \(\emptyset\).

\section{Differential and Integral Calculus}
Calculus of Differential and integral.

\paragraph{Examples}

Sum: \(\sum\limits_{i=1}^{\infty}\).

Prod: \(\prod\limits_{i=1}^{\infty}\).

Integral: \(\int_{x=0}^{\infty} f(x) d{x}\).

Circular integral: \(\oint_{s} f(s) d{s}\)

Partial: \(\frac{\partial}{\partial x} f\).

\section{Notions}
Special notions.

\paragraph{Examples}

Underbrace: \(\underbrace{A+B+C+ \dots +Z}_{\text{26}}\).

Overbrace: \(\overbrace{A+B+C+ \dots +Z}^{\text{26}}\).

Leftarrow: \(\xleftarrow[bottom]{top}\).

Rightarrow: \(\xrightarrow[bottom]{top}\).

Tops: \(\vec{a}, \hat{a}, \widehat{a}, \grave{a}, \bar{a}, \dot{a}, \ddot{a}, \check{a}, \tilde{a}, \widetilde{a}\)

Laplace: \(\nabla a\)

Dots: \(\dot{a}, \ddot{a}\)

Tail: \(a^{'}\)

\section{Greek letters}
Greek letters

\paragraph{Lowercase letters}
\(alpha-\alpha, beta-\beta, gamma-\gamma, delta-\delta, epsilon-\epsilon\)

\(varepsilon-\varepsilon, zeta-\zeta, eta-\eta, theta- \theta, vartheta-\vartheta\)

\(iota-\iota, kappa-\kappa, lambda-\lambda, mu-\mu, nu-\nu\)

\(xi-\xi, pi-\pi, varpi-\varpi, rho-\rho, varrho-\varrho\)

\(sigma-\sigma, varsigma-\varsigma, tau-\tau, upsilon-\upsilon, phi-\phi\)

\(varphi-\varphi, chi-\chi, psi-\psi, omega-\omega\)

\paragraph{Uppercase letters}
\(Gamma-\Gamma, Delta-\Delta, Theta-\Theta, Lambda-\Lambda, Xi-\Xi, Pi-\Pi, Sigma-\Sigma, Upsilon-\Upsilon, Phi-\Phi, Psi-\Psi, Omega-\Omega\)

\end {document}